Msc Thesis Figures

### 2025-02-19 docs/msc_thesis_figures.Rmd
add up

```{r}
networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  filter(species %in% c("MAAM", "URAM")) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, names_glue = "ts_{timestep}_{.value}", values_from = values) %>% 
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values) %>% 
  select(-starts_with("ts")) %>% 
  pivot_wider(names_from = metric, values_from = percent_change) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>% 
  select(-c(code_run, climate)) %>%
  select(species, scenario, starts_with("overall"), numNodes, numLinks, meanAreaQuality, meanCost) %>%

>>>>

```{r}
networks %>% 
  filter(scenario != 37, timestep %in% c(2,10)) %>% 
  filter(species %in% c("MAAM", "URAM")) %>% 
  pivot_longer(numNodes:overallECnatal, names_to = "metric", values_to = "values") %>% 
  select (species, iteration, timestep, code_run, climate, metric, values) %>% 
  group_by(species, timestep, code_run, climate, metric) %>% 
  summarise(values = mean(values)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = timestep, values_from = values) %>% # names_glue = "ts_{timestep}_{.value}",
  mutate(percent_change = (ts_10_values - ts_2_values)/ts_2_values) %>% 
  select(-starts_with("ts")) %>% 
  pivot_wider(names_from = metric, values_from = percent_change) %>% 
  mutate(code_run = fct_relevel(code_run, c("BAU", "BAUR", "CP", "CPR", "CPTR"))) %>% 
  arrange(code_run) %>% 
  mutate(climate = fct_relevel(climate, c("baseline", "RCP 8.5")))  %>% 
  arrange(code_run, climate) %>% 
  mutate(scenario = paste(code_run, climate)) %>%
  arrange(code_run, climate, scenario) %>% 
  select(-c(code_run, climate)) %>%
  select(species, scenario, starts_with("overall"), numNodes, numLinks, meanAreaQuality, meanCost) %>%
